Incentivizing Exploration with Unbiased History

### 2018-11-01 model.tex
Moved Greedy into Warmup, and started revising.
Moved a macro to the main file.

\newcommand{\SubH}[1]{H_{#1}} % subhistory
\newcommand{\AnonSubH}[1]{H^{\texttt{anon}}_{#1}} % subhistory

@@

We allow a much more permissive model, characterized by the following assumption:

@@

>>>>

@@

We allow a much more permissive model, characterized by the following assumption:%
\footnote{In what follows, we make this assumption without further notice.}

@@

We use $O_K(\cdot)$ notation to hide the dependence on parameter $K$, and $\tilde O(\cdot)$ notation to hide polylogarithmic factors. We denote $[T]= \{1,2 \LDOTS T\}$.
